---
title: 'Post-Acute Sequelae of SARS-CoV-2 Infection: A Systematic Review'
output:
  html_document:
    df_print: paged
  pdf_document: default
  html_notebook: default
---
#https://www.r-graph-gallery.com/boxplot.html

# LOAD REQUIRED PACKAGES AND FUNCTIONS -----------------------------------------
```{r, message=FALSE, echo=FALSE,warning=FALSE}
library(olsrr) # linear regression
library(tidyverse) # general stuff
library(hrbrthemes) # pretty plots
library(ggplot2) # pretty plots
library(plotly) # interactive plots
library(gapminder) # interactive plots
library(pastecs) # stat.desc
library(metafor) # for meta-analysis: mixed-effects logistic and Poisson regression models
library(meta) # meta-regression, GLMM, forest plots,(subgroup) meta-analyses.
library(sp) # spatial data
library(rgdal) #  projection/transformation operations for shapefiles
library(sf) # Simple Features for R
library(rnaturalearth)
library(tmap) # cool maps
library(ggpubr) # 'ggplot2' Based Publication Ready Plots
library(ggpmisc) #Miscellaneous Extensions to 'ggplot2'
library(spData)
library(cowplot)# plot grid
library(ggsci)
library(RColorBrewer)
library(ggrepel)
library(readxl)
library(dplyr)
library(reshape)
library(viridis)

library(ggrepel)
library(colorspace)
library(colorblindr)
```


```{r setup, include=FALSE,warning=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,warning =F)
```



# read data -----------------------------------------
```{r,echo=FALSE,warning=FALSE}
rm(list=ls())
#data=read.csv("AnalysisPASC2.csv")
data=read.csv("AnalysisPASC3.csv")
arrange(data, desc(-Period))
```

# Pooled analysis: All -----------------------------------------
```{r,echo=FALSE,warning=FALSE}
l1=is.na(data$PASC_overall)
dat=data[!l1,]
```


# Meta-regression

```{r}

f <- data %>%
  arrange(desc(sample_size)) %>%
  ggplot(aes(x = FU_d, y = Rates)) +
  #ggplot(aes(x = Period, y = Rates, fill=Period))+  
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  #geom_boxplot(show.legend = F)+
  geom_point(aes(fill = Period,  size = sample_size), shape = 21, alpha = .7) +
  colorblindr::scale_fill_OkabeIto(name = "Period") +
  scale_size(name = "COVID-19 Survivors",
             range = c(2, 10), breaks = c(10000, 50000, 100000, 150000, 200000, 250000)) +
  #annotate("text", label = "p==0.33~~R^{2}==0.00", x = 120, y = 95, parse = T) +
  geom_text_repel(aes(label = Country), size = 2.5) +
  facet_wrap(~ "Follow-up") +
  labs(x = "Follow-up time from baseline (Days)", y = "PASC frequency (%)")  +
  guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

f
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_Time.pdf", width = 10, height = 8)

```


# Box Plot: Evolution

```{r}
ff <- data %>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = FU_d, y = Rates)) +
  ggplot(aes(x = Period, y = Rates, fill=Period))+  
   #ggplot(aes(x = fct_reorder(Period, Rates, FUN = median, .desc = T, na.rm=T), y = Rates))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(show.legend = F)+
  geom_point(aes(fill = Period), shape = 21, alpha = .7) +
  colorblindr::scale_fill_OkabeIto(name = "Follow-up") +
  facet_wrap(~ "PASC stratified by follow-up period ") +
  labs(x = "Period", y = "PASC Frequency (%)")  +
  guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

ff
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure2.pdf", width = 10, height = 8)

ggpubr::ggarrange(f, ff, ncol = 2, labels = c('A', 'B'), nrow=1, common.legend = F, legend = "none")
ggsave("figs/Figure1.pdf", width = 10, height = 10)


```

```{r}

df=group_by(data, Period) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates, probs = 0.25),
    median = median(Rates, na.rm = TRUE),
    q3 = quantile(Rates, probs = 0.75)
    
  )

df


```
# Box Plot: Income

```{r}
g20 <- data %>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = FU_d, y = Rates)) +
  ggplot(aes(x = fct_reorder(Income, Rates, FUN = median, .desc =TRUE, na.rm=T), y = Rates,fill=Income))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(show.legend = F)+
  geom_point(aes(fill = Income), shape = 21, alpha = .7) +
  colorblindr::scale_fill_OkabeIto(name = "Income level") +
  facet_wrap(~ "PASC by income level") +
  labs(x = "Income level", y = "PASC frequency (%)")  +
  guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

g20
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure2.pdf", width = 10, height = 8)



df=group_by(data, Income) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates, probs = 0.25),
    median = median(Rates, na.rm = TRUE),
    q3 = quantile(Rates, probs = 0.75)
    
  )

df

```

# Box Plot: Hospitalized

```{r}

data=read.csv("AnalysisPASC3.csv")

l1=is.na(data$COVID19_Hospitolized_perc)
dat=data[!l1,]
g21 <- dat %>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = FU_d, y = Rates)) +
   ggplot(aes(x = fct_reorder(Hospitalized_cat, Rates, FUN = median, .desc =TRUE, na.rm=T), y = Rates,       fill=Hospitalized_cat))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(show.legend = F)+
  geom_point(aes(fill = Hospitalized_cat), shape = 21, alpha = .7) +
  colorblindr::scale_fill_OkabeIto(name = "Proportion\nHospitalized") +
  facet_wrap(~ "PASC by proportion hospitalized") +
  labs(x = "Proportion hospitalized", y = "PASC Frequency (%)")  +
  guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

g21


df=group_by(dat, Hospitalized_cat) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates, probs = 0.25),
    median = median(Rates, na.rm = TRUE),
    q3 = quantile(Rates, probs = 0.75)
    
  )

df


```



# Box Plot: Hospitalized

```{r}

dat=read.csv("AnalysisPASC3.csv")


g22 <- dat %>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = FU_d, y = Rates)) +
  ggplot(aes(x = fct_reorder(NOS_Cat, Rates, FUN = median, .desc =TRUE, na.rm=T), y = Rates, fill=NOS_Cat))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(show.legend = F)+
  geom_point(aes(fill = NOS_Cat), shape = 21, alpha = .7) +
  colorblindr::scale_fill_OkabeIto(name = "Study quality\n score") +
  facet_wrap(~ "PASC by study quality score") +
  labs(x = "Study quality score", y = "PASC Frequency (%)")  +
  guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

g22


df=group_by(dat, NOS_Cat) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates, probs = 0.25),
    median = median(Rates, na.rm = TRUE),
    q3 = quantile(Rates, probs = 0.75)
    
  )

df

ggpubr::ggarrange(g20,g21, g22,  ncol = 2, nrow=2, labels=c("A", "B", "C"), common.legend = F, legend = "none")
ggsave("figs/suppl.pdf", width = 15, height = 15)


```




# Box Plot: WHO groups

```{r,fig.height=6, fig.width=10, echo=FALSE,warning=FALSE}
g2 <- data %>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = FU_d, y = Rates)) +
  ggplot(aes(x = WHO, y = Rates, fill=WHO))+  
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(show.legend = F)+
  geom_point(aes(fill = WHO), shape = 21, alpha = .7) +
  colorblindr::scale_fill_OkabeIto(name = "WHO") +
  facet_wrap(~ "PASC by WHO regions") +
  labs(x = "WHO regions", y = "PASC Frequency (%)")  +
  guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

g2
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure2_WHO.pdf", width = 10, height = 8)



df=group_by(data, WHO) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates, probs = 0.25),
    median = median(Rates, na.rm = TRUE),
    q3 = quantile(Rates, probs = 0.75)
    
  )

df

```


 # constitutional symptoms-------------------------------------
```{r,fig.height=5, fig.width=10, echo=FALSE,warning=FALSE, eval=T}
data=read.csv("AnalysisPASC3.csv")
l=reshape(data, 
          varying=c("fatigue_or_muscle_weakness_n","joint_pain","Myalgia","Flu.like.sxs_rhinitis", "fever","Pain","weight.loss._5perc"),
          
          v.names="Constitutional",
          
          times=c("Fatigue or muscle weakness","Arthralgia", "Myalgia","Flu like symptoms", "Fever","General pain", "Weight loss"),   
          
          timevar="Outcome",
          new.row.names = 1:1000,
          direction="long")


l1=is.na(l$Constitutional)
dat=l[!l1,]

dat$Rates2=dat$Constitutional/dat$sample_size*100



E <- dat%>%
  #arrange(desc(Period)) %>%
  ggplot(aes(x = Outcome, y = Rates2)) +
  #ggplot(aes(x = reorder(times, Rates2, FUN = median, .desc =TRUE, na.rm=T), y = Rates2))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(outlier.shape = NA,outlier.size =0)+
  geom_jitter(color="black", size=0.9, alpha=0.4, shape=5) +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  coord_flip()+
  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "General symptoms") +
  labs(x = "", y = "PASC frequency (%)")  +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

E
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_Con.pdf", width = 20, height = 8)


df=group_by(dat, Outcome) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates2, probs = 0.25),
    median = median(Rates2, na.rm = TRUE),
    q3 = quantile(Rates2, probs = 0.75)
    
  )

df


```





# PULMONARY-------------------------------------
```{r,fig.height=5, fig.width=10, echo=FALSE,warning=FALSE, eval=T}
data=read.csv("AnalysisPASC3.csv")
l=reshape(data, varying=list(samplesize = c("sample_size", "chest_imaging_abnormality_N", "pulmonary_diffusion_abnormality_N","sample_size","sample_size","sample_size","sample_size","sample_size"),
                            pulmonary = c("cough", "chest_imaging_abnormality_n", "pulmonary_diffusion_abnormality._less_80perc_n","Restriction_.spirometry","Dyspnea","Fibrosis", "ground_glass_opacification","O2.use")), 
          v.names=c("N", "n"), 
          # that was needed after changed 'varying' arg to a list to allow 'times' 
          direction="long",  
          times=1:8,        # substitutes number for T1 and T2
          timevar="times")  # to name the time col

l$times=factor(l$times)




levels(l$times)=c("Cough", "Chest imaging abnormality", "Pulmonary diffusion abnormality","Restriction patterns on spirometry","Dyspnea","Lung fibrosis","Ground glass opacification", "Oxygen use")

l1=is.na(l$n)
datx=l[!l1,]

l2=is.na(datx$N)
dat=datx[!l2,]
dat$Rates2=dat$n/dat$N*100


library(forcats)

C <- dat%>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = times, y = Rates2)) +
  ggplot(aes(x = fct_reorder(times, Rates2, FUN = median, .desc =TRUE, na.rm=T), y = Rates2))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(outlier.shape = NA,outlier.size =0)+
  geom_jitter(color="black", size=0.9, alpha=0.4, shape=5) +
  coord_flip()+
  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "Respiratory Disorders") +
  labs(x = "", y = "PASC frequency (%)")  +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

C
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_p.pdf", width = 20, height = 8)


df=group_by(dat, times) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates2, probs = 0.25),
    median = median(Rates2, na.rm = TRUE),
    q3 = quantile(Rates2, probs = 0.75)
    
  )

df

```



# Cardiac-------------------------------------
```{r,fig.height=5, fig.width=10, echo=FALSE,warning=FALSE}
data=read.csv("AnalysisPASC3.csv")
l=reshape(data, 
          varying=c("Chest_pain","palpitation"),
          
          v.names="Cardiac",
          
          times=c("Chest pain","Palpitation"),  
          
          timevar="Outcome",
          new.row.names = 1:1000,
          direction="long")


l1=is.na(l$Cardiac)
dat=l[!l1,]
dat$Rates2=dat$Cardiac/dat$sample_size*100



FF <- dat%>%
  #arrange(desc(Period)) %>%
  ggplot(aes(x = Outcome, y = Rates2)) +
  #ggplot(aes(x = reorder(times, Rates2, FUN = median, .desc =TRUE, na.rm=T), y = Rates2))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(outlier.shape = NA,outlier.size =0)+
  geom_jitter(color="black", size=0.9, alpha=0.4, shape=5) +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  coord_flip()+
  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "Cardiac Disorders") +
  labs(x = "", y = "PASC frequency (%)")  +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

FF
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_c.pdf", width = 20, height = 8)


df=group_by(dat, Outcome) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates2, probs = 0.25),
    median = median(Rates2, na.rm = TRUE),
    q3 = quantile(Rates2, probs = 0.75)
    
  )

df

```



# PSYCHIATRIC/mental health-------------------------------------
```{r,fig.height=5, fig.width=10, echo=FALSE,warning=FALSE, eval=T}
data=read.csv("AnalysisPASC3.csv")
l=reshape(data, varying=list(samplesize = c("anxiety_or_depression_N", "sample_size","sample_size","sample_size"),
                            pulmonary = c("anxiety_or_depression_n", "PTSD", "GAD","sleep_abnormality_n")), 
          v.names=c("N", "n"), 
          # that was needed after changed 'varying' arg to a list to allow 'times' 
          direction="long",  
          times=1:4,        # substitutes number for T1 and T2
          timevar="times")  # to name the time col

l$times=factor(l$times)



levels(l$times)=c("Depression", "PTSD", "Generalized anxiety disorder","Sleep disorder")

l1=is.na(l$n)
datx=l[!l1,]

l2=is.na(datx$N)
dat=datx[!l2,]
dat$Rates2=dat$n/dat$N*100




B <- dat%>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = times, y = Rates2)) +
  ggplot(aes(x = fct_reorder(times, Rates2, FUN = median, .desc =TRUE, na.rm=T), y = Rates2))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(outlier.shape = NA,outlier.size =0)+
  geom_jitter(color="black", size=0.9, alpha=0.4, shape=5) +
  coord_flip()+
  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "Mental Health Disorders") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  labs(x = "", y = "PASC frequency (%)")  +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

B
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_mental.pdf", width = 20, height = 8)

df=group_by(dat, times) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates2, probs = 0.25),
    median = median(Rates2, na.rm = TRUE),
    q3 = quantile(Rates2, probs = 0.75)
    
  )

df


```




# FUNCTIONAL MOBILITY-------------------------------------
```{r,fig.height=4, fig.width=8, echo=FALSE,warning=FALSE}
data=read.csv("AnalysisPASC3.csv")
l=reshape(data, 
          varying=c("exercise.tolerance.decreased","Mobility.decline", "Functional.Impairment"),
          
          v.names="Functional_Mobility",
          
          times=c("Decreased exercise tolerance ","Mobility decline","Functional impairment"),  
          
          timevar="Outocome",
          new.row.names = 1:1000,
          direction="long")


l1=is.na(l$Functional_Mobility)
dat=l[!l1,]

dat$Rates2=dat$Functional_Mobility/dat$sample_size*100



D <- dat%>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = times, y = Rates2)) +
  ggplot(aes(x = fct_reorder(Outocome, Rates2, FUN = median, .desc =TRUE, na.rm=T), y = Rates2))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(show.legend = F)+
  geom_boxplot(outlier.shape = NA,outlier.size =0)+
  geom_jitter(color="black", size=0.9, alpha=0.4, shape=5) +
  coord_flip()+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "Mobility Impairment") +
  labs(x = "", y = "PASC Prevalence (%)")  +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

D
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_Functional.pdf", width = 20, height = 8)



df=group_by(dat, Outocome) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates2, probs = 0.25),
    median = median(Rates2, na.rm = TRUE),
    q3 = quantile(Rates2, probs = 0.75)
    
  )

df



```



# Neuro-------------------------------------
```{r,fig.height=5, fig.width=10, echo=FALSE,warning=FALSE}
data=read.csv("AnalysisPASC3.csv")
l=reshape(data, 
          varying=c("headache","Mnesinc.complaints","Concentration","Cognitive.Impairment","Taste_disorder","smell_disorder"),
          
          v.names="Neurocognition",
          
          times=c("Headache","Memory deficits","Difficulty concentrating", "Cognitive impairment","Taste disorder (ageusia or dysgeusia)","Smell disorder (anosmia)"),  
          
          timevar="Outocome",
          new.row.names = 1:1000,
          direction="long")


l1=is.na(l$Neurocognition)
dat=l[!l1,]

dat$Rates2=dat$Neurocognition/dat$sample_size*100



A <- dat%>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = times, y = Rates2)) +
  ggplot(aes(x = fct_reorder(Outocome, Rates2, FUN = median, .desc =TRUE, na.rm=T), y = Rates2))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(outlier.shape = NA,outlier.size =0)+
  geom_jitter(color="black", size=0.9, alpha=0.4, shape=5) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  coord_flip()+
  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "Neurologic Disorders") +
  labs(x = "", y = "PASC frequency (%)")  +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

A

ggsave("figs/Figure_Neuro.pdf", width = 20, height = 8)


df=group_by(dat, Outocome) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates2, probs = 0.25),
    median = median(Rates2, na.rm = TRUE),
    q3 = quantile(Rates2, probs = 0.75)
    
  )

df


```



# GI-------------------------------------
```{r,fig.height=5, fig.width=10, echo=FALSE,warning=FALSE}
data=read.csv("AnalysisPASC3.csv")
l=reshape(data, 
          varying=c("Digestive.Disorders","Diarrhea_vomiting","Abdominal.Pain","decreased_appetite"),
          
          v.names="GI",
          
          times=c("Digestive Disorders (any)","Diarrhea & vomiting", "Abdominal pain", "Decreased appetite"),  
          
          timevar="Outcome",
          new.row.names = 1:1000,
          direction="long")


l1=is.na(l$GI)
dat=l[!l1,]

dat$Rates2=dat$GI/dat$sample_size*100




G <- dat%>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = times, y = Rates2)) +
  ggplot(aes(x = fct_reorder(Outcome, Rates2, FUN = median, .desc =TRUE, na.rm=T), y = Rates2))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(outlier.shape = NA,outlier.size =0)+
  geom_jitter(color="black", size=0.9, alpha=0.4, shape=5) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  coord_flip()+
  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "Digestive Disorders") +
  labs(x = "", y = "PASC frequency (%)")  +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

G
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_GI.pdf", width = 20, height = 8)


df=group_by(dat, Outcome) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates2, probs = 0.25),
    median = median(Rates2, na.rm = TRUE),
    q3 = quantile(Rates2, probs = 0.75)
    
  )

df


```


# Derm-------------------------------------
```{r,fig.height=3, fig.width=6, echo=FALSE,warning=FALSE}
data=read.csv("AnalysisPASC3.csv")
l=reshape(data, 
          varying=c("Skin_rash","hair_loss"),
          
          v.names="Derm",
          
          times=c("Skin rash","Hair loss"),  
          
          timevar="Outcome",
          new.row.names = 1:1000,
          direction="long")


l1=is.na(l$Derm)
dat=l[!l1,]

dat$Rates2=dat$Derm/dat$sample_size*100



H <- dat%>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = times, y = Rates2)) +
  ggplot(aes(x = fct_reorder(Outcome, Rates2, FUN = median, .desc =TRUE, na.rm=T), y = Rates2))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(outlier.shape = NA,outlier.size =0)+
  geom_jitter(color="black", size=0.9, alpha=0.4, shape=5) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  coord_flip()+
  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "Skin Disorder") +
  labs(x = "", y = "PASC frequency (%)")  +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

H
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_dERM.pdf", width = 20, height = 8)


df=group_by(dat, Outcome) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates2, probs = 0.25),
    median = median(Rates2, na.rm = TRUE),
    q3 = quantile(Rates2, probs = 0.75)
    
  )

df


```




# ENT------------------------------------
```{r,fig.height=2, fig.width=5, echo=FALSE,warning=FALSE}
data=read.csv("AnalysisPASC3.csv")
l=reshape(data, 
          varying=c("Sorethroat"),
          
          v.names="ENT",
          
          times=c("Sorethroat"),  
          
          timevar="Outcome",
          new.row.names = 1:1000,
          direction="long")


l1=is.na(l$ENT)
dat=l[!l1,]

dat$Rates2=dat$ENT/dat$sample_size*100




I <- dat%>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = times, y = Rates2)) +
  ggplot(aes(x = fct_reorder(Outcome, Rates2, FUN = median, .desc =TRUE, na.rm=T), y = Rates2))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot(outlier.shape = NA,outlier.size =0)+
  geom_jitter(color="black", size=0.9, alpha=0.4, shape=5) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  coord_flip()+
  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "ENT Disorders") +
  labs(x = "", y = "PASC frequency (%)")  +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

I
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_ENT.pdf", width = 20, height = 8)


df=group_by(dat, Outcome) %>%
  summarise(
    count = n(),
    q1 = quantile(Rates2, probs = 0.25),
    median = median(Rates2, na.rm = TRUE),
    q3 = quantile(Rates2, probs = 0.75)
    
  )

df


```


# Mean and sd for age: 54 (8.9)

```{r}

mean(data$mean_age, na.rm = T) # 54.35849
sd(data$mean_age, na.rm = T) #8.916481
```



# Median and IQR for Score: 6.0 (5 to 7)

```{r}

#summary(data$Total.NOS)
summary(data$male_perc)
```



# Percentage hospitalized

```{r, eval=F}

data=read.csv("AnalysisPASC3.csv")

l1=is.na(data$COVID19_Hospitolized_perc)
dat=l[!l1,]

g_p <- dat%>%
  #arrange(desc(Period)) %>%
  #ggplot(aes(x = times, y = Rates2)) +
  ggplot(aes(x = fct_reorder(Hospitalized_cat, Rates, FUN = median, .desc =TRUE, na.rm=T), y = Rates))+ 
  #geom_smooth(se = F, method = "lm", size = 1.5) +
  geom_boxplot()+
  #geom_point(aes(), shape = 5, alpha = .7) +
  scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
  theme_ipsum() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +

  #colorblindr::scale_fill_OkabeIto(name = "times") +
  facet_wrap(~ "Hospitalized") +
  labs(x = "", y = "PASC frequency (%)")  +
  #guides(fill = guide_legend(override.aes = list(size = 3.5))) +
  theme_bw(base_size = 14) +
  theme(strip.text = element_text(face = "bold", size = 13))

g_p
#ggpubr::ggarrange(g1, g2, ncol = 1, common.legend = T, legend = "right")
ggsave("figs/Figure_ENT.pdf", width = 20, height = 8)

# Plot
dat %>%
  ggplot( aes(x=Hospitalized_cat, y=Rates, fill=Hospitalized_cat)) +
    geom_boxplot() +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_jitter(color="black", size=0.9, alpha=0.4) +
    theme_ipsum() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("A boxplot with jitter") +
    xlab("")


```





```{r}

mean(dat$COVID19_Hospitolized_perc, na.rm=T)
mean(dat$COVID19_Hospitolized_perc, na.rm=T)

```


```{r}


ggpubr::ggarrange(A, B, C,E,FF,G,H,I,  ncol = 2, nrow=4, common.legend = F, legend = "none", labels =c('A','B','C','D','E','F','G','H','I'))

ggsave("figs/Figure2.pdf", width = 15, height = 15)


```







